SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-09-12 scipy-1.0/paper.tex
Start fleshing out 'SciPy begins' section

@@

Travis O
Pearu
-
Gary Strangman
%
%https://mail.python.org/pipermail/scipy-dev/2001-November/000088.html
%
%
Eric and Travis V

@@

- Aug 20, 2001
Eric Jones announced

@@

@@

    Special Functions (Bessel, hanker, Airy, etc.)
    Signal/Image Processing
    2D Plotting capabilities
    Integration
    ODE solvers
    Optimization (simplex, BFGS, Netwon-CG, etc.)
    Genetic Algorithms
    Numeric -> C++ expression compiler
    Parallel programming tools
    Splines and Interpolation
    And other stuff.
\end{verbatim}
\caption{Excerpt from first release announcement.}
\end{figure}

>>>>

% Paul Dubois, CDAT
% https://mail.python.org/pipermail/numpy-discussion/2001-May/000645.html

% Perry Greenfield, Hubble
% https://conference.scipy.org/scipy2011/slides/greenfield_keynote_astronomy.pdf
%
% Note: plotting was important for them, so they eventually
% funded development on Matplotlib.

% Numeric, even though written by grad students, became critical for
% large scale endeavors

@@

%With a rich programming environment and a numerical array object in
%place, the time was ripe for the development of a full scientific
%software stack.

% PhD Mayo Clinic, started faculty position at BYU in 2001
By the late 90s, Travis Oliphant, a PhD student at the Mayo Clinic,
released a number of packages\footnote{https://web.archive.org/web/19990125091242/http://oliphant.netpedia.net:80/}\footnote{https://web.archive.org/web/20001206213500/http://oliphant.netpedia.net:80/} that built on top of the Numeric array
package, and provided algorithms for signal processing, special
functions, sparse matrices, quadrature, optimization, and Fast Fourier
Transforms, and more.  One of these packages, Multipack, was a set of
extension modules that wrapped Fortran and C libraries such as
ODEPACK, QUADPACK, and MINPACK, to solve and minimize nonlinear
equations, integrate differential equations, and fit splines (the
latter implemented by Pearu Peterson).  Robert Kern, then an
undergraduate student (and currently a SciPy core developer), provided
compilation instructions under Windows.
% 2001 PhD Tallinn Technical University
Around the same time, Pearu Peterson, a PhD student from Estonia,
released f2py\footnote{https://mail.python.org/pipermail/numpy-discussion/2000-September/000243.html}, a command line tool for binding Python and Fortran
codes.
% Graduated 1999, Duke
Eric Jones, while a graduate student at Duke, wrote a number of
packages to support his dissertation, including a parallel job
scheduler and genetic optimizer.
% Graduated 1998, PhD from Brown, 97–99 postdoc at Harvard Medical
% School; at Harvard ever since
%
% https://mail.python.org/pipermail/scipy-dev/2001-November/000088.html
%
Gary Strangman, a postdoctoral fellow at Harvard Medical School,
published several descriptive and inferential statistical routines\footnote{https://web.archive.org/web/20001022231108/http://www.nmr.mgh.harvard.edu/Neural\_Systems\_Group/gary/python.html}.

In 2001, Eric Jones and Travis Vaught founded Enthought Scientific
Computing Solutions (now Enthought, Inc.) in Austin, Texas.  In an
effort to simplify the tool stack, they created the SciPy project,
centered around the SciPy library which would subsume all the
above-mentioned packages.

@@

- Aug 20, 2001
Eric Jones announced \ref{fig:announce-0.1}

@@

NumPy 2005

@@

    Special Functions (Bessel, hanker, Airy, etc.)
    Signal/Image Processing
    2D Plotting capabilities
    Integration
    ODE solvers
    Optimization (simplex, BFGS, Netwon-CG, etc.)
    Genetic Algorithms
    Numeric -> C++ expression compiler
    Parallel programming tools
    Splines and Interpolation
    And other stuff.
\end{verbatim}
\caption{Excerpt from first release announcement.}\label{fig:announce-0.1}
\end{figure}
